SpatialEpi

### 2021-06-10 README.Rmd
refactoring expected function
Trivial change

[![Travis-CI Build Status](https://travis-ci.org/rudeboybert/SpatialEpi.svg?branch=master)](https://travis-ci.org/rudeboybert/SpatialEpi)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/SpatialEpi)](http://cran.r-project.org/package=SpatialEpi)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/SpatialEpi)](http://www.r-pkg.org/pkg/SpatialEpi)

@@

@@

```{r, fig.height=6.5}
plotmap(output$post_map$high_area, sp.obj)
```

>>>>

[![R-CMD-check](https://github.com/rudeboybert/SpatialEpi/workflows/R-CMD-check/badge.svg)](https://github.com/rudeboybert/SpatialEpi/actions)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/SpatialEpi)](http://cran.r-project.org/package=SpatialEpi) [![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/SpatialEpi)](http://www.r-pkg.org/pkg/SpatialEpi)

@@

Note: You may need to install the `cpp11` for all C++ code to compile correctly.

@@

```{r, fig.height=6.5}
plotmap(output$post.map$high.area, sp.obj)
```
